\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(d2).

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of \textit{Equation 12}, we may have:

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}

As It is known from \textbf{d1} that $f(2n) = \Theta(f(n))$, which implies $f(2n) = O(f(n))$. Also it is given that $f(n) = O(n^c)$. Together, we shall infer $f(2n) = O(n^c)$ due to the transitivity property of $\Theta$- and $O$-notations.

>>>>

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of problem statement, we may have:

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d2) If $f(n) = O(n^k)$, then $f(2n) = O(n^k)$}

For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.

Since $f(n) = O(n^k)$, we must have $0 \leq f(n) \leq cn^k$ for $n \geq n_0$ and a $c$ for $c \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:

\begin{gather}
    0 \leq f(2n) \leq c(2n)^k \nonumber \\
    \Rightarrow 0 \leq f(2n) \leq c\cdot (2)^k \cdot n^k \\
    \Rightarrow 0 \leq f(2n) \leq c' \cdot n^k \ \ \ \text{where $c' = c\cdot (2)^k$}
\end{gather}

Thus we may conclude if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$.
